No proof nets for \capsabbrev{mll} with units

### 2014-05-26 main/LICS.tex
Reverse text/diagram ordering in octopus roll lemma
I find it easier to follow the proof if the text precedes the
associated diagram.

\begin{proof}
Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
%
The rewiring path will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.

@@

\noindent
1.\quad The initial configuration is illustrated above. 
%
Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
%
The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.

@@

\noindent
2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$.

@@

\noindent
3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.

@@

\displayOcto{\octorollA2}

\noindent
7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration.
%
\end{proof}

>>>>

\begin{proof}
Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $V=X\tn Y$.
%
The rewiring path will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.

\noindent
1.\quad The initial configuration is illustrated below.
%
Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
%
The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.

@@

\noindent
2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$:

@@

\noindent
3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$:

@@

@@

\noindent
7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration:

\displayOcto{\octorollA2}
%
\end{proof}
